---
title: 'CyTargetLinker use case 1: PPI Compound / Disease Extension'
author: "mkutmon"
date: "July 7, 2019"
version: 2.0
---
  
################################
# Tested with 
# Cytoscape version 3.7.1
# CyTargetLinker version 4.1.0
# stringApp version 1.4.2
# R version 3.5.3
# RCy3 version 2.0.88
################################

# Step 0: Set up environment
```{r setup, include=FALSE}
if(!"RCy3" %in% installed.packages()){
  install.packages("RCy3")
}
library(RCy3)
```

## Set working directory
```{r set working directory}
if(!"knitr" %in% installed.packages()){
  install.packages("knitr")
}
library(knitr)
knitr:::input_dir()
```

## check cytoscape connection
```{r test connection}
cytoscapePing()
if("cytargetlinker" %in% commandsHelp("")) print("Success: the CyTargetLinker app is installed") else print("Warning: CyTargetLinker app is not installed. Please install the CyTargetLinker app before proceeding.")
if("string" %in% commandsHelp("")) print("Success: the STRING app is installed") else print("Warning: STRING app is not installed. Please install the STRING app before proceeding.")
```

# Step 1: Load PPI from STRING
```{r}
string.cmd = 'string disease query disease="Rett syndrome " cutoff=0.4 species="Homo sapiens" limit=20'
commandsRun(string.cmd)
```

# Step 2: Extend network with compound (ChEMBL) and disease (OMIM) information
## Before you run this section, please make sure to unzip the ChEMBL link set in the LinkSets folder. The file is to big to upload to github without being zipped. 
```{r}
chembl <- file.path(getwd(), "LinkSets", "chembl_23_hsa_20180126.xgmml")
omim <- file.path(getwd(), "LinkSets", "rare-disease-gene-associations-hsa-20180411.xgmml")
CTLextend.cmd = paste('cytargetlinker extend idAttribute="display name" linkSetFiles="', chembl, ',', omim, '" network=current', sep="")
commandsRun(CTLextend.cmd)
layoutNetwork()
```

# Step 4: Load viusal style
```{r}
vizstyle.file <- file.path(getwd(), "VizStyles", "use-case1-style.xml")
LoadStyle.cmd = paste('vizmap load file file="',vizstyle.file,'"', sep="")
commandsRun(LoadStyle.cmd)

setVisualStyle("CTL Disease Compound Network")
```

# Step 5: Save images and session
```{r}
png.file <- file.path(getwd(), "Disease-Compound-Rett-Network.png")
exportImage(png.file,'PNG')
session.file <- file.path(getwd(), "Disease-Compound-Rett-Network.cys")
saveSession(session.file)
```


